WGS fastq2vcf walkthrough

### 2021-11-05 WGS-Full-Walkthrough.Rmd
Added WGS tutorials
Added WGS image

---
layout: default
title: WGS fastq2vcf walkthrough
parent: Whole Genome Resequencing
grand_parent: Choosing a PopGenomics Approach
editor_options: 
  chunk_output_type: console
---

@@

}
```
<!-- <img src="./Pop1_17291100XcoveragePlot10000.png" width="500">  -->

>>>>

---
title: WGS fastq2vcf walkthrough

---

@@

}
```
![Output](images/Pop1_17291100XcoveragePlot10000.png)

<!-- <img src="./Pop1_17291100XcoveragePlot10000.png" width="500">  -->
